Reproduciable Research - Peer Assignment 1
========================================================
## Loading and preprocessing the data


```{r}
x<-read.csv("activity.csv")
y<-complete.cases(x)
w<-x[y,]

```

##  Total number of steps taken per day

```{r Total no of steps, fig.width=6,fig.height=6}
z<-aggregate(steps~date,w,sum)
hist(z$steps,main="Total no of steps",xlab="No of steps",col="blue")

```
### Mean of total steps
```{r}
mean(z$steps)
```
### Median of total steps
```{r}
median(z$steps)
```
## Average daily activity pattern


```{r Average daily activity pattern, fig.width=10,fig.height=8}
temp<-aggregate(steps~interval,w,mean)
temp$interval<-strptime(sprintf("%04d", as.numeric(as.character(temp$interval))), "%H%M")
plot(temp$interval,temp$steps,type="l",main="Trend of steps",xlab="Timer Interval",ylab="No of steps")

```

### 5-minute interval contains the maximum number of steps

```{r}
temp[(temp$steps==max(temp$steps)),]

```
## Imputing missing values

### Total number of missing values in the dataset 
```{r}
table(y)

```

###  Filling in all of the missing values & creation of new dataset.
```{r}
library(rrcovNA)
xx<-as.data.frame(impSeq(x))

```

### Histogram of the total number of steps taken each day 
```{r Total no of steps after imputaion, fig.width= 6,fig.height= 6}
zz<-aggregate(steps~date,xx,sum)
hist(zz$steps,main="Total no of steps after imputation",xlab="No of steps",col="blue")

```

### Mean of total steps
```{r}
mean(zz$steps)

```
### Median of total steps
```{r}
median(zz$steps)

```

## Activity patterns between weekdays and weekends

### New data set with week levels

```{r}
xxx<-x
xxx$steps<-xx$steps
xxx$date<-as.Date(xxx$date)
xxx$week<-as.factor(weekdays(xxx$date))
library(plyr)
library(ggplot2)
xxx$week<-mapvalues(xxx$week, from = c("Friday","Monday","Thursday","Tuesday","Wednesday","Sunday","Saturday"), to = c( "weekday","weekday","weekday","weekday","weekday","weekend","weekend"))

```

### Plot of activity pattern in weekday & weekend

```{r Activity pattern in weekday & weekend}
df<-aggregate(steps~interval+week,xxx,mean)
ggplot(df,aes(interval,steps))+geom_line()+facet_grid(week~.)

```
